***
after checking the same for the BRFSS datasets of 2011 and 2013 as they had these exact predictors, we found that the result is more or less same with .01 difference range for AuC values and FpR and FnR are also varying within +/- 3%
hence we wanted to see if AuC can be kept same if the whole dataset is randomly downsampled sampled first and then the above method is applied..in this case we made the imbalance ration of calibrate and test set as 4.74:1 each and the ttrain set as 3:1 and we observed a drastic change at the confusion matrix entries DESPITE the AuC being the same as well as the top 5 candidates in the VARIMP plot..hence we can conclude that explanable AI is needed to be used to check if truely the dataset lacks enough pure mutually exclusive behavioural features or is it just because of the model design and the class imbalance of 24:1 for stroke response..going further into this direction was out of our scope for this research. We found that our pre-determined criterion of "purely behavioural features" were found most in numbers for only these 3 datasets of BRFSS - 2011,2012&2013 out of available ones after 2011 before the submission of this work. Datasets before 2011 used a different survey methodoly hence we excluded them from our study (for details please consult https://www.cdc.gov/brfss/annual_data/annual_data.htm ) . 
***

***
downsample whole input data to 4.74 : 1 imbalance
***

```{r}
#stroke1 <- read.csv("stroke_clean.csv")
set.seed(1122)
library(dplyr)
stroke_tmp <- stroke1
random_pool <- sample(1:nrow(stroke1), nrow(stroke1) / 1.25, replace = FALSE)
random_pool_tmp <- data.frame(random_pool)
random_pool_tmp <-  subset(random_pool_tmp, stroke_tmp$CVDSTRK3[random_pool] < 1 )
stroke_tmp <- stroke_tmp[ -random_pool_tmp$random_pool[1:nrow(random_pool_tmp)], ]
stroke1_downsampled <- stroke_tmp
rm(stroke_tmp,random_pool_tmp)

```

```{r}
summary(as.factor(stroke1_downsampled$CVDSTRK3))
```
```{r}
stroke1_downsampled.h2o <- as.h2o(stroke1_downsampled)

covtype.splits <- h2o.splitFrame(stroke1_downsampled.h2o, ratios = 
                                   c(0.89, 0.01)
                                 , seed = 1122)
train12_downsampled.h2o <- covtype.splits[[1]]
calibrate12_downsampled.h2o <- covtype.splits[[2]]
test12_downsampled.h2o <- covtype.splits[[3]]
```

```{r}
summary(as.factor(train12_downsampled.h2o$CVDSTRK3))
nrow(train12_downsampled.h2o)
train12_downsampled <- as.data.frame(train12_downsampled.h2o)
#stroke_keep <- stroke1_downsampled.h2o
```

***
Random_Downsample_Train_Set
***

```{r}
set.seed(1122)
library(dplyr)
stroke_tmp <- train12_downsampled
random_pool <- sample(1:nrow(train12_downsampled), nrow(train12_downsampled) / 19.50, replace = FALSE)
random_pool_tmp <- data.frame(random_pool)
random_pool_tmp <-  subset(random_pool_tmp, stroke_tmp$CVDSTRK3[random_pool] < 1 )
stroke_tmp <- stroke_tmp[ -random_pool_tmp$random_pool[1:nrow(random_pool_tmp)], ]
train12_downsampled.h2o <- as.h2o(stroke_tmp)
rm(stroke_tmp,random_pool_tmp, train12_downsampled)
```

```{r}
summary(as.factor(train12_downsampled.h2o$CVDSTRK3))
```

***
model building
***

```{r}
colnames(train12_downsampled.h2o)
```

```{r}
x.indep <- c(2:16)
y.dep <- c(1)
```

***
grid search
***

```{r}
gbm_params2 <- list(col_sample_rate = seq(0.3, 0.7, 1.0),
                   max_depth = seq(5, 7, 13)
                    ,
                   learn_rate = seq(0.01, 0.1, 0.001)
                    #sample_rate = seq(0.5, 1.0, 0.1),
                    #col_sample_rate = seq(0.1, 1.0, 0.1)
                   )
 # gbm_params2 <- list(learn_rate = seq(0.01, 0.1, 0.01),
 #                     max_depth = seq(2, 10, 1),
 #                     sample_rate = seq(0.5, 1.0, 0.1),
 #                     col_sample_rate = seq(0.1, 1.0, 0.1))
 # search_criteria <- list(strategy = "RandomDiscrete", max_models = 36, seed = 1)
search_criteria <- list(strategy = "RandomDiscrete", max_models = 10, seed = 1122)
```

```{r}
train12_downsampled.h2o[,1] <- as.factor(train12_downsampled.h2o[,1])
colnames(train12_downsampled.h2o)
summary(train12_downsampled.h2o$CVDSTRK3)
```

```{r}
gbm_grid_calib_downsampled_2012_70_downsampled <- h2o.grid("gbm", x = x.indep, y = y.dep,
                      grid_id = "gbm_grid_calib_downsampled_2", 
                      training_frame = train12_downsampled.h2o,
                                            ntrees = 500,
                      seed = 1122,
                      nfolds = 5,
                      hyper_params = gbm_params2,
                      search_criteria = search_criteria
                      )
```

```{r}
gbm_gridperf2 <- h2o.getGrid(grid_id = "gbm_grid_calib_downsampled_2",
                             sort_by = "auc",
                             decreasing = TRUE)
print(gbm_gridperf2)
# best GBM model by AUC
best_gbm_2012_70_downsampled <- h2o.getModel(gbm_gridperf2@model_ids[[1]])
```
***
best GBM model
***

```{r}
best_gbm_perf2 <- h2o.performance(model = best_gbm_2012_70_downsampled,
                                  newdata = test12_downsampled.h2o)
(best_gbm_perf2)
h2o.auc(h2o.performance(best_gbm_2012_70_downsampled, train12_downsampled.h2o))
```
***
UNCALIBRATED RESULTS
***

```{r}
h2o.auc((h2o.performance(best_gbm_2012_70_downsampled, test12_downsampled.h2o)))
h2o.confusionMatrix(best_gbm_2012_70_downsampled, test12_downsampled.h2o)
```

***
Calibration - Platt Scaling
***

```{r}
summary(as.factor(calibrate12_downsampled.h2o$CVDSTRK3), exact_quantiles=TRUE)
```

```{r}
set.seed(1122)
predicted.calib <- h2o.predict(best_gbm_2012_70_downsampled, calibrate12_downsampled.h2o)
manual.calib.input <- cbind(as.data.frame(predicted.calib$p1), as.data.frame(calibrate12_downsampled.h2o$CVDSTRK3))
    colnames(manual.calib.input) <- c("p1", "response")
manual.calib.input.h2o <- as.h2o(manual.calib.input)
gbm_calib_downsampled_model_12_70_platt <- h2o.glm( x = "p1", y = "response", training_frame = manual.calib.input.h2o  , family = "binomial" )
    ```
    
    
```{r}
predicted.test12_downsampled <- h2o.predict(best_gbm_2012_70_downsampled, test12_downsampled.h2o)
manual.test12_downsampled.input <- cbind(as.data.frame(predicted.test12_downsampled$p1), as.data.frame(test12_downsampled.h2o$CVDSTRK3))
colnames(manual.test12_downsampled.input) <- c("p1", "response")
manual.test12_downsampled.input.h2o <- as.h2o(manual.test12_downsampled.input)
h2o.auc(h2o.performance(gbm_calib_downsampled_model_12_70_platt , manual.test12_downsampled.input.h2o))
h2o.confusionMatrix(gbm_calib_downsampled_model_12_70_platt, manual.test12_downsampled.input.h2o, metrics=list("f0point5", "f1", "f2", "precision","accuracy"))    
```

***
CALIBRATED RESULT
***

```{r}
h2o.auc(h2o.performance(gbm_calib_downsampled_model_12_70_platt , manual.test12_downsampled.input.h2o))
    h2o.confusionMatrix(gbm_calib_downsampled_model_12_70_platt, manual.test12_downsampled.input.h2o#, metrics=list("f0point5", "f1", "f2", "precision","accuracy")
                        ) # table 2
    plot(h2o.performance(gbm_calib_downsampled_model_12_70_platt , manual.test12_downsampled.input.h2o), type = "roc") # figure 5
    
```

```{r fig.height=6, fig.width=10}
h2o.varimp_plot(best_gbm_2012_70_downsampled, num_of_features = 20) # figure 6 & table 3
```

***
{True_Negative_Extraction and False_Positive_Extraction} and {False_Negative_Extraction and True_Positive_Extraction}
***

```{r}
prediction_frame <- h2o.predict(gbm_calib_downsampled_model_12_70_platt , manual.test12_downsampled.input.h2o)
prediction_frame
```

```{r}
confusion_matrix_prep_frame <- test12_downsampled.h2o
confusion_matrix_prep_frame$predict <- prediction_frame$predict
confusion_matrix_prep_frame$p0 <- prediction_frame$p0
confusion_matrix_prep_frame$p1 <- prediction_frame$p1
confusion_matrix_prep_frame <- as.data.frame(confusion_matrix_prep_frame)
FP_set_2012_downsampled <- subset(confusion_matrix_prep_frame, confusion_matrix_prep_frame$predict == 1 & confusion_matrix_prep_frame$CVDSTRK3 == 0)
FN_set_2012_downsampled <- subset(confusion_matrix_prep_frame, confusion_matrix_prep_frame$predict == 0 & confusion_matrix_prep_frame$CVDSTRK3 == 1)
TN_set_2012_downsampled <- subset(confusion_matrix_prep_frame, confusion_matrix_prep_frame$predict == 0 & confusion_matrix_prep_frame$CVDSTRK3 == 0)
TP_set_2012_downsampled <- subset(confusion_matrix_prep_frame, confusion_matrix_prep_frame$predict == 1 & confusion_matrix_prep_frame$CVDSTRK3 == 1)
FP_set_2012_downsampled
TN_set_2012_downsampled
FN_set_2012_downsampled
TP_set_2012_downsampled
```

***
behaviour of predictor model on X.CHLDCNT
***

```{r}
library(ggplot2)
qplot(x = X.CHLDCNT, y = p0, data = FN_set_2012_downsampled, geom = "point")
```

***
SHAP VALUES
***

```{r}
predict_auc <- h2o.predict_contributions(best_gbm_2012_70_downsampled, test12_downsampled.h2o)
predict_auc
```

