***
dataset_split(after loading h2o library)
***

```{r}
stroke1.h2o <- as.h2o(stroke1)
rm(train12.h2o, test12.h2o, calibrate12.h2o)
covtype.splits <- h2o.splitFrame(stroke1.h2o, ratios = 
                                   c(0.89, 0.01)
                                 , seed = 1122)
train12.h2o <- covtype.splits[[1]]
calibrate12.h2o <- covtype.splits[[2]]
test12.h2o <- covtype.splits[[3]]
```

```{r}
summary(as.factor(train12.h2o$CVDSTRK3))
nrow(train12.h2o)
train12 <- as.data.frame(train12.h2o)
#stroke_keep <- stroke1.h2o
```

***
Random_Downsample_Train_Set
***

```{r}
set.seed(1122)
library(dplyr)
stroke_tmp <- train12
random_pool <- sample(1:nrow(train12), nrow(train12) / 1.25, replace = FALSE)
random_pool_tmp <- data.frame(random_pool)
random_pool_tmp <-  subset(random_pool_tmp, stroke_tmp$CVDSTRK3[random_pool] < 1 )
stroke_tmp <- stroke_tmp[ -random_pool_tmp$random_pool[1:nrow(random_pool_tmp)], ]
train12.h2o <- as.h2o(stroke_tmp)
rm(stroke_tmp,random_pool_tmp, train12)

```

```{r}
summary(as.factor(train12.h2o$CVDSTRK3))
summary(as.factor(stroke1$CVDSTRK3)) # figure 3
```

***
model building
***

```{r}
colnames(train12.h2o)
```

```{r}
x.indep <- c(2:16)
y.dep <- c(1)
```

***
grid search
***

```{r}
gbm_params2 <- list(col_sample_rate = seq(0.3, 0.7, 1.0),
                   max_depth = seq(5, 7, 13)
                    ,
                   learn_rate = seq(0.01, 0.1, 0.001)
                    #sample_rate = seq(0.5, 1.0, 0.1),
                    #col_sample_rate = seq(0.1, 1.0, 0.1)
                   )
 # gbm_params2 <- list(learn_rate = seq(0.01, 0.1, 0.01),
 #                     max_depth = seq(2, 10, 1),
 #                     sample_rate = seq(0.5, 1.0, 0.1),
 #                     col_sample_rate = seq(0.1, 1.0, 0.1))
 # search_criteria <- list(strategy = "RandomDiscrete", max_models = 36, seed = 1)
search_criteria <- list(strategy = "RandomDiscrete", max_models = 10, seed = 1122)
```

```{r}
train12.h2o[,1] <- as.factor(train12.h2o[,1])
colnames(train12.h2o)
summary(train12.h2o$CVDSTRK3)
```

```{r}
gbm_grid_calib_2012_70 <- h2o.grid("gbm", x = x.indep, y = y.dep,
                      grid_id = "gbm_grid_calib_1", 
                      training_frame = train12.h2o,
                                            ntrees = 500,
                      seed = 1122,
                      nfolds = 5,
                      hyper_params = gbm_params2,
                      search_criteria = search_criteria
                      )
```

```{r}
gbm_gridperf2 <- h2o.getGrid(grid_id = "gbm_grid_calib_1",
                             sort_by = "auc",
                             decreasing = TRUE)
print(gbm_gridperf2)
# best GBM model by AUC
best_gbm_2012_70 <- h2o.getModel(gbm_gridperf2@model_ids[[1]])
```
***
best GBM model
***

```{r}
best_gbm_perf2 <- h2o.performance(model = best_gbm_2012_70,
                                  newdata = test12.h2o)
(best_gbm_perf2)
h2o.auc(h2o.performance(best_gbm_2012_70, train12.h2o))
```
***
UNCALIBRATED RESULTS
***

```{r}
h2o.auc((h2o.performance(best_gbm_2012_70, test12.h2o)))
h2o.confusionMatrix(best_gbm_2012_70, test12.h2o)
```

***
Calibration - Platt Scaling
***

```{r}
summary(as.factor(calibrate12.h2o$CVDSTRK3), exact_quantiles=TRUE)
```

```{r}
set.seed(1122)
predicted.calib <- h2o.predict(best_gbm_2012_70, calibrate12.h2o)
manual.calib.input <- cbind(as.data.frame(predicted.calib$p1), as.data.frame(calibrate12.h2o$CVDSTRK3))
    colnames(manual.calib.input) <- c("p1", "response")
manual.calib.input.h2o <- as.h2o(manual.calib.input)
gbm_calib_model_12_70_platt <- h2o.glm( x = "p1", y = "response", training_frame = manual.calib.input.h2o  , family = "binomial" )
    ```
```{r}
predicted.test12 <- h2o.predict(best_gbm_2012_70, test12.h2o)
manual.test12.input <- cbind(as.data.frame(predicted.test12$p1), as.data.frame(test12.h2o$CVDSTRK3))
colnames(manual.test12.input) <- c("p1", "response")
manual.test12.input.h2o <- as.h2o(manual.test12.input)
h2o.auc(h2o.performance(gbm_calib_model_12_70_platt , manual.test12.input.h2o))
h2o.confusionMatrix(gbm_calib_model_12_70_platt, manual.test12.input.h2o, metrics=list("f0point5", "f1", "f2", "precision","accuracy"))    
```

***
CALIBRATED RESULT
***

```{r}
h2o.auc(h2o.performance(gbm_calib_model_12_70_platt , manual.test12.input.h2o))
    h2o.confusionMatrix(gbm_calib_model_12_70_platt, manual.test12.input.h2o#, metrics=list("f0point5", "f1", "f2", "precision","accuracy")
                        )
    plot(h2o.performance(gbm_calib_model_12_70_platt , manual.test12.input.h2o), type = "roc")
    
```

```{r fig.height=6, fig.width=10}
h2o.varimp_plot(best_gbm_2012_70, num_of_features = 20)
```

***
{True_Negative_Extraction and False_Positive_Extraction} and {False_Negative_Extraction and True_Positive_Extraction}
***

```{r}
prediction_frame <- h2o.predict(gbm_calib_model_12_70_platt , manual.test12.input.h2o)
prediction_frame
```

```{r}
confusion_matrix_prep_frame <- test12.h2o
confusion_matrix_prep_frame$predict <- prediction_frame$predict
confusion_matrix_prep_frame$p0 <- prediction_frame$p0
confusion_matrix_prep_frame$p1 <- prediction_frame$p1
confusion_matrix_prep_frame <- as.data.frame(confusion_matrix_prep_frame)
FP_set_2012 <- subset(confusion_matrix_prep_frame, confusion_matrix_prep_frame$predict == 1 & confusion_matrix_prep_frame$CVDSTRK3 == 0)
FN_set_2012 <- subset(confusion_matrix_prep_frame, confusion_matrix_prep_frame$predict == 0 & confusion_matrix_prep_frame$CVDSTRK3 == 1)
TN_set_2012 <- subset(confusion_matrix_prep_frame, confusion_matrix_prep_frame$predict == 0 & confusion_matrix_prep_frame$CVDSTRK3 == 0)
TP_set_2012 <- subset(confusion_matrix_prep_frame, confusion_matrix_prep_frame$predict == 1 & confusion_matrix_prep_frame$CVDSTRK3 == 1)
FP_set_2012
TN_set_2012
FN_set_2012
TP_set_2012
```

***
behaviour of predictor model on X.CHLDCNT
***

```{r}
library(ggplot2)
qplot(x = X.CHLDCNT, y = p0, data = FN_set_2012, geom = "point")
```

***
SHAP VALUES : "The Shapley value is the average of the marginal contributions across all permutations. The Shapley values consider all possible permutations, thus SHAP is a united approach that provides global and local consistency and interpretability" //Lundberg, Scott M., and Su-In Lee. "A unified approach to interpreting model predictions." Advances in neural information processing systems. 2017.
***

```{r}
predict_auc <- h2o.predict_contributions(best_gbm_2012_70, test12.h2o)
predict_auc
```
