***
upload h2o only after the original BRFSS dataset is removed if RStudio is used as it eats up too much of the global memory causing the machine to hang up as was the case of this case on a UBUNTU-16.04 LTS, 8GB RAM,4 core
***

```{r}
library(h2o)
localH2O <- h2o.init(nthreads = -1)
#h2o.getVersion()
#h2o_context(sc)
```


***
check for outlier
***

***
Step A. remove NaN
***

```{r}
stroke1$AVEDRNK2 <- replace(stroke1$AVEDRNK2, which(is.na(stroke1$AVEDRNK2)), mean(stroke1$AVEDRNK2, na.rm=T))
stroke1$SCNTWRK1 <- replace(stroke1$SCNTWRK1, which(is.na(stroke1$SCNTWRK1)), mean(stroke1$SCNTWRK1, na.rm=T))
stroke1$FVBEANS <- replace(stroke1$FVBEANS, which(is.na(stroke1$FVBEANS)), mean(stroke1$FVBEANS, na.rm=T))
stroke1$FVGREEN <- replace(stroke1$FVGREEN, which(is.na(stroke1$FVGREEN)), mean(stroke1$FVGREEN, na.rm=T))
stroke1$FVORANG <- replace(stroke1$FVORANG, which(is.na(stroke1$FVORANG)), mean(stroke1$FVORANG, na.rm=T))
stroke1$SSBSUGR1 <- replace(stroke1$SSBSUGR1, which(is.na(stroke1$SSBSUGR1)), mean(stroke1$SSBSUGR1, na.rm=T))
stroke1$SSBFRUT1 <- replace(stroke1$SSBFRUT1, which(is.na(stroke1$SSBFRUT1)), mean(stroke1$SSBFRUT1, na.rm=T))
stroke1$FRUIT1 <- replace(stroke1$FRUIT1, which(is.na(stroke1$FRUIT1)), mean(stroke1$FRUIT1, na.rm=T))
stroke1$FRUITJU1 <- replace(stroke1$FRUITJU1, which(is.na(stroke1$FRUITJU1)), mean(stroke1$FRUITJU1, na.rm=T))
stroke1$VEGETAB1 <- replace(stroke1$VEGETAB1, which(is.na(stroke1$VEGETAB1)), mean(stroke1$VEGETAB1, na.rm=T))
stroke1$SLEPTIME <- replace(stroke1$SLEPTIME, which(is.na(stroke1$SLEPTIME)), mean(stroke1$SLEPTIME, na.rm=T))
```

```{r}
summary(stroke1)
```

```{r}
stroke1$X.CHLDCNT <- replace(stroke1$X.CHLDCNT, which(is.na(stroke1$X.CHLDCNT)), 0)
stroke1$X.TOTINDA <- replace(stroke1$X.TOTINDA, which(is.na(stroke1$X.TOTINDA)), 0)
stroke1$X.SMOKER3 <- replace(stroke1$X.SMOKER3, which(is.na(stroke1$X.SMOKER3)), 0)
stroke1$USENOW3 <- replace(stroke1$USENOW3, which(is.na(stroke1$USENOW3)), 0)
```

```{r}
stroke1$CVDSTRK3 <- ifelse(stroke1$CVDSTRK3==1, 1, 0)
```

```{r}
stroke1$X.CHLDCNT<-as.factor(stroke1$X.CHLDCNT)
stroke1$X.TOTINDA <- as.factor(stroke1$X.TOTINDA)
stroke1$X.SMOKER3 <- as.factor(stroke1$X.SMOKER3) 
stroke1$USENOW3 <- as.factor(stroke1$USENOW3)
stroke1$CVDSTRK3 <- as.factor(stroke1$CVDSTRK3)
```

```{r}
summary(stroke1)
```

```{r}
summary(stroke1$CVDSTRK3)
```

***
Step 2. cooks distance
***

```{r}
mod_cook <- glm(CVDSTRK3 ~.,family=binomial(link ='logit'), data=stroke1)
summary(mod_cook)
```

```{r}
y.train <- 1
x.train <- c(2:16)
data <- train12.h2o
mod_cook_h2o <- h2o.glm(x.train, y.train, data, seed=112, family = "binomial")
```

```{r}
mod_cook_h2o
```

```{r}
mean(cooksd)
```

```{r}
cooksd = cooks.distance(mod_cook)
```

```{r height =5, width =2}
plot(cooksd, pch="*", cex=2, main="Influential Obs by Cooks distance")  
abline(h = 4*mean(cooksd, na.rm=T), col="black") # 4*mean is standard practice but not hard set
text(x=1:length(cooksd)+1, y=cooksd, labels=ifelse(cooksd>20*mean(cooksd, na.rm=T),names(cooksd),""), col="red")  
```

***
influential outliers
***

```{r}
influential <- as.numeric(names(cooksd)[(cooksd > 4*mean(cooksd, na.rm=T))])
summary(as.factor(stroke1[influential, ]$CVDSTRK3))
```

***
cooks distance here due to the
imbalance shows most positive cases
as outlier which is why we normalized
cooks distance to 2*(10) times the
mean as start is 0.000 end is 0.025,
i.e, 25 times the space, ie,
mean_space@0.0012, but as in this
case mean~0, i.e, less than .005 =>
mean is taken@4*(5) times, 4 is the
prescribed but not hard set value
consulted from multiple sources
***

```{r height =5, width =2}
plot(cooksd, pch="*", cex=2, main="Influential Obs by Cooks distance")  
abline(h = 20*mean(cooksd, na.rm=T), col="black")  
text(x=1:length(cooksd)+1, y=cooksd, labels=ifelse(cooksd>20*mean(cooksd, na.rm=T),names(cooksd),""), col="red")  
```

```{r}
influential <- as.numeric(names(cooksd)[(cooksd > 20*mean(cooksd, na.rm=T))]) 
summary(as.factor(stroke1[influential, ]$CVDSTRK3))
```

***
thus both the checks show that only
for both cases only negligible number
of negative stroke responses are
influential outliers 
***